---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.asp = 0.618, collapse=TRUE) 
```

### In-class exercises
### Unit 1: Getting Started

***

### Exercise 1.1

Creat a vector of 5 numbers (any numbers will do). Multiply the vector by 2 and print out the results. Try adding 7 to the vector. Does this just add 7 to the first number in the vector or to every element of the vector? Make another vector with any 3 numbers and add this to your first vector, then save the results into a new variable. Are the results what you expected?

```{r}
dat = c(1,3,5,7,9)
dat*2
dat+7

dat2 = c(2,4,6)
dat3 = dat+dat2
dat3
```

### Exercise 1.2

Use the `world_oceans` data frame that we have built and add a new column for ocean volume. Use the area and average depth variables to create a back-of-the-envelope volume calculation in $km^3$ (watch your units!). Then create a new data frame that holds just the subset of oceans that you have personally traveled to. 

```{r}
world_oceans = data.frame(oceans = c("Atlantic", "Pacific", "Indian", "Arctic", "Southern"),
                           area_km2 = c(77e6, 156e6, 69e6, 14e6, 20e6),
                           avg_depth_m = c(3926, 4028, 3963, 3953, 4500))

world_oceans$volume_km3 = world_oceans$area_km2 * (world_oceans$avg_depth_m * 0.001)
my_oceans = world_oceans[c(1,2),]
```

### Exercise 1.3

Look at the R Documentation for the `signif()` function by typing `?signif` into the Console or searching for "signif" in the Help pane in the lower right corner of RStudio. Use signif() to reduce the number of digits in your world_oceans volume data to 3 significant digits then calculate the mean ocean volume. Try doing this in the opposite order by first calculating the mean ocean volume, then reducing your answer to just 3 significant digits. How different are the 2 answers? Which one is a better estimation? 

```{r}
mean(world_oceans$volume_km3) # True answer
signif(mean(world_oceans$volume_km3), digits=3) # better estimation
mean(signif(world_oceans$volume_km3, digits=3)) # throws away information before calculation

signif(mean(world_oceans$volume_km3), digits=3) - mean(world_oceans$volume_km3) 
mean(signif(world_oceans$volume_km3, digits=3)) - mean(world_oceans$volume_km3)
```

