---
title: "Rmd_Example"
author: "MSCI 599"
output: html_document
---

# Big heading
## Medium heading
### Small heading
#### Tiny heading

This is an example of an .Rmd file. We can define code chunks by using three grave accents, followed by curly brackets around r. A code chunk looks like this;

```{r}
x = c(1,2,3)
y = c(2,4,6)
```

If we write code that produces output, such as this:

```{r}
plot(x,y)
```

The output will appear inline in the rendered document right after the code chunk. If you don’t want the code of a particular code chunk to appear in the final document, but still want to show the output (e.g. a plot), then you can include echo = FALSE in the code chunk instructions:

```{r, echo=FALSE}
plot(x,y)
```

There are plenty of other code chunk instructions you can inlcude in the curly braces to customize your `.Rmd` file. 

***

Bulleted lists:

My family's fave pizza toppings:

- pineapple
- bacon

***

My pet's in order of how much I like them:

1. Nana (dog)
2. Wheezer (cat)
3. Napoleon (jerkface)
